Reanalysis Step 4: Outcome Analysis with Three-Way Interaction

### 2025-08-17 reanalysis-4-outcome_analysis.qmd
twang

# Calculate derived statistics
manual_effects <- manual_effects |>
  mutate(
    CI_Lower = Log_Odds - 1.96 * SE,
    CI_Upper = Log_Odds + 1.96 * SE,
    OR = exp(Log_Odds),
    Z_stat = Log_Odds / SE,
    P_Value = 2 * pnorm(-abs(Z_stat))
  ) |>
  mutate(across(c(Log_Odds, SE, CI_Lower, CI_Upper, OR), ~round(., 4))) |>
  mutate(P_Value = format.pval(P_Value, digits = 4, eps = 0.0001)) |>
  select(-Z_stat)

>>>>

# Calculate derived statistics for non-NA values
manual_effects <- manual_effects |>
  mutate(
    CI_Lower = ifelse(!is.na(Log_Odds) & !is.na(SE), Log_Odds - 1.96 * SE, NA),
    CI_Upper = ifelse(!is.na(Log_Odds) & !is.na(SE), Log_Odds + 1.96 * SE, NA),
    OR = ifelse(!is.na(Log_Odds), exp(Log_Odds), NA),
    P_Value = ifelse(!is.na(Log_Odds) & !is.na(SE) & SE > 0, 
                    2 * pnorm(-abs(Log_Odds / SE)), NA)
  )

# Format the results
manual_effects <- manual_effects |>
  mutate(across(c(Log_Odds, SE, CI_Lower, CI_Upper, OR), ~round(., 4))) |>
  mutate(P_Value = ifelse(!is.na(P_Value), 
                          format.pval(P_Value, digits = 4, eps = 0.0001), 
                          NA))

# Check if we have valid results
n_valid <- sum(!is.na(manual_effects$Log_Odds))
if (n_valid == 0) {
  message("Warning: No valid manual effect calculations")
} else if (n_valid < nrow(manual_effects)) {
  message("Warning: Some manual effect calculations contain NA values (", 
          nrow(manual_effects) - n_valid, " out of ", nrow(manual_effects), ")")
}
